---
title: "AalborgRUG finances"
author: "Ege Rubak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Income

Only source of income so far is the sponsorship by R Consortium (and we do not
expect that to change anytime soon):
```{r}
old <- options(stringsAsFactors = FALSE)
income <- data.frame(date = "2017-10-23",
                     text = "R Consortium",
                     DKK = 1106.86)
income[2,] <- data.frame("2018-06-27", "R Consortium", 1119.06)
income[3,] <- data.frame("2019-07-25", "R Consortium", 1173.02)
knitr::kable(income)
```

## Expenses

Biggest expense is meetup.com where we started on a basic plan but had to upgrade
when we hit 50+ members. The subscription info I have from meetup.com so far is:

- Your last payment of US$29.94 was received on Sep 30, 2017.
- Your next payment of $47.94 for a 6 month Unlimited plan will be charged on Mar 30, 2018.
- Your last payment of US$47.94 was received on Apr 1, 2018.
- Your next payment of $47.94 for a 6 month Unlimited plan will be charged on Sep 30, 2018.

**NOTE:** With the new R Consortium RUG Program the subscription is paid for by
R Consortium, so this expense will no longer appear.

The only expense we expect now is to drinks and snacks
for meetups that aren't sponsored by anyone.
```{r}
expenses <- data.frame(date = "2017-10-03", text = "meetup.com", DKK = 192.10)
expenses[2,] <- data.frame("2017-11-13", "Snacks and drinks", 340.85)
expenses[3,] <- data.frame("2017-12-04", "Foreign bank transfer fee", 35.00)
expenses[4,] <- data.frame("2018-04-04", "meetup.com", 295.09)
expenses[5,] <- data.frame("2018-06-27", "Foreign bank transfer fee", 30.00)
expenses[6,] <- data.frame("2018-10-01", "Snacks and drinks", 506.25)
expenses[7,] <- data.frame("2019-04-23", "Snacks and drinks", 521.08)
expenses[8,] <- data.frame("2019-07-25", "Foreign bank transfer fee", 30.00)
knitr::kable(expenses)
```

## Current status

At the moment it all boils down to:
```{r}
(profit <- sum(income$DKK) - sum(expenses$DKK))
```
Since we have a `r ifelse(profit>0, "profit we are all happy", "deficit we should be worried")`. 

## Budget

No, we don't have a budget. Fingers crossed.

```{r}
options(old)
```
